\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{needspace} 

% Custom section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}
  {\centering\bfseries\large} % centered + bold + large
  {} % no label
  {0em} % no indent
  {\underline} % underline the title text itself




% Name and contact info
\begin{document}

\begin{center}
    {\LARGE \textbf{Caden William Clements}}\\
    \href{mailto:cwc09262@gmail.com}{cwc09262@gmail.com} } \\
    (484) 651 - 9363 \\
    \href{https://main.d2ugd62ymj09qk.amplifyapp.com}{Portfolio Website} \textbar{} \href{https://github.com/cwc09262}{Github} \\
    Villanova, PA 19085 \\
   
    \textit{Aspiring Natural Language Processing Academic with a strong foundation in cybersecurity and applied machine learning. }
\end{center}

% Education
\section*{Education}
\textbf{Villanova University} - \textit{(In Progress)} \hfill Villanova, Pennsylvania \\
M.S in Computer Science \hfill August 2025 - \textit{Current} \\
GPA: \textit{TBD}

\textbf{Oxford Study Aborad Program (OSAP)} \hfill Oxford, United Kingdom \\
Oxford Study Abroad Student \hfill Fall 2024 

\begin{itemize}[noitemsep]
    \item Completed an Oxford Style tutorial on the teachings and theology of C.S. Lewis.
    \item Completed an Oxford Style tutorial on the principles of programming languages.
\end{itemize}

\textbf{Eastern University} \hfill St. Davids, Pennsylvania \\
B.S. in Computer Science \& Data Science with Minor in History\hfill August 2021 -- 
May 2025 \\
GPA: 3.67 / 4.00 \hfill Dean's List Student
\section*{Relevant Coursework}
Machine Learning, Natural Language Processing, Cryptography, Programming Languages, Data Science Research Methods, Algorithms, Cybersecurity


% Research
\section{Research}

\subsection*{Applied - Practical}
\textbf{Cyber Security Intern} -- United States Coast Guard \hfill Staten Island, New York \\
\textit{May 2023 -- July 2023} \hfill Internship
\begin{itemize}[noitemsep]
    \item Researched maritime cyber hygiene and simulated a cyber attack with Brendan Dolan.
    \item Enhanced New York Harbor cybersecurity protocols and developed a cyber outreach website.
\end{itemize}

\subsection*{Theoretical } 
\textbf{Research Symposium Presentation} \hfill Eastern University - April 2025 
\begin{itemize}[noitemsep]
	\item Presented research conducted about the machine learning models trained revealing differing translation purposes between the Psalter and Book of Psalms from the Orthodox Christian Church. Studied the Principal Component Analysis of a TF-IDF matrix. 
\end{itemize} 


% Teaching
\section{Teaching}


\textbf{Teaching Assistant} \hfill Eastern University - \textit{Multiple Semesters} \\
Computer Science \& Data Science
\begin{itemize}[noitemsep]
	\item Held Office Hours
	\item Assisted in lectures, created assignments, and graded them
	\item Built automatic graders for assignments
\end{itemize}

\textbf{Teaching Assistant} \hfill Eastern University - \textit{One Semester} \\
History\\



% Industry
\section*{Industry}
\textbf{Computer Science Intern} -- United States Coast Guard \hfill Staten Island, New York 
\textit{June 2025  --August 2025} \hfill Internship 
\begin{itemize}[noitemsep]
    \item Collaborated with staff to improve a cyber outreach tool for the maritime industry.
    \item Researched cargo movement within the port and assessed key risks to operations.
    \item Input data into an existing dashboard to help trace petrochemical supply chains.
    \item Analyzed terminal dependencies, including cargo blending and pipeline operations.
    \item Learned to engage port partners effectively and document workflow processes.
    \item Developed skills in maintaining cybersecurity standards within maritime operations.
\end{itemize} 
\needspace{5\baselineskip}
\textbf{Cyber \& Website Intern} -- United States Coast Guard \hfill Staten Island, New York \\
\textit{June 2024 -- August 2024} \hfill Internship
\begin{itemize}[noitemsep]
    \item Built website for Vessel Agents to use that covers every different problem they may have.
	\item Rebuild Cyber Outreach tool with better information and personally designed graphics
\end{itemize} \

% Projects
\section*{Projects}
\href{https://github.com/cwc09262/st_david-s-beacon}{\textbf{Saint David's Beacon}} \hfill \textit{Spring 2025}
\begin{itemize}[noitemsep]
    \item Studied and applied mathematical foundations of machine learning.    
    \begin{itemize}[label=--]
        \item Term Frequency–Inverse Document Frequency, Principal Component Analysis, Cosine Similarity
    \end{itemize}
    \item Built a custom data pipeline to clean and structure text from multiple translations of the Psalms.
    \item Trained and evaluated transformer-based models (e.g., all-mpnet-base-v2) to generate embeddings for similarity search.
    \item Deployed the search engine as a Flask web application for interactive querying and visualization of results.
\end{itemize}
\href{https://cwc09262.github.io/Astronomy_Observation_NoteBook/}{\textbf{Astronomy Observations Website}} \hfill Spring 2024
\begin{itemize}
    \item At the end of taking observation for an astronomy lab, I was tasked with building a compiled notebook for submission. I choose to build a website for my submission. 
\end{itemize}
\textbf{API Behavior Machine Learning Model} \hfill Fall 2023
\begin{itemize}[noitemsep]
    \item Focused on cleaning API behavior data in my first machine learning project.
    \item Built a simple model and gained initial exposure to the ML pipeline.
\end{itemize}

\textbf{Coffee Bean Analytics} \hfill Spring 2023 
\begin{itemize}[noitemsep]
	\item Conducted a thorough analysis of a coffee bean dataset, exploring the impact of variables such as altitude, processing method, variety, and region/country on coffee quality, resulting in a detailed project report and presentation.
\end{itemize}
% Skills
\section*{Skills}
\begin{tabular}{ll}
    Programming: & Python, Java, C++, HTML/CSS, JavaScript, R \\
    Tools: & Git, Docker, LaTeX, VS Code, Linux, R Studio, Jupyter Notebooks\\
    Languages: & English (fluent)
\end{tabular}

\section*{Awards \& Honors}
\begin{tabular}{p{0.65\textwidth} r}
    \textbf{Certificate of Merit} -- United States Coast Guard & Aug 2025 \\
    \textbf{Heroic Endeavor Award} -- Eastern University & May 2025 \\
    \textbf{Certificate of Merit} -- United States Coast Guard & Aug 2024 \\
    \textbf{Sigma Zeta Honor Society} -- Eastern University & Apr 2023 -- May 2025 \\
    \textbf{Eagle Scout} -- Troop 241, Knauers, PA & Oct 2018 \\
\end{tabular}


\end{document}